---
title: "Tradeoffs between PPR carbon sequestration and biodiversity"
author:
  - name: Samuel G. Woodman
    orcid: 0000-0001-9725-5867
    email: samuel.woodman@uleth.ca
    corresponding: true
    affiliation: 
      - name: University of Lethbridge
  - name: Lauren E. Bortolotti
    email: l_bortolotti@ducks.ca
    corresponding: false
    affiliation: 
      - name: Ducks Unlimited Canada
  - name: James E. Paterson
    email: j_paterson@ducks.ca
    corresponding: false
    affiliation: 
      - name: Ducks Unlimited Canada
  - name: Pascal Badiou
    email: p_badiou@ducks.ca
    corresponding: false
    affiliation: 
      - name: Ducks Unlimited Canada
  - name: Matthew J Bogard
    email: matthew.bogard@uleth.ca
    corresponding: false
    affiliation: 
      - name: University of Lethbridge
format:
  html:
    toc: true
    toc-location: left
    comments:
      hypothesis: true
    embed-resources: true
    fig-width: 8
    fig-height: 6
  docx: default
  pdf: default
editor: visual
editor_options: 
  chunk_output_type: console
execute: 
  echo: false
  warning: false
---

```{r}
library(tidyverse)
library(here)
library(ggtext)
library(patchwork)
library(ggpubr)
library(gridtext)
library(ggpmisc)
library(ggsignif)
library(rstatix)
library(gt)
library(simplermarkdown)
library(knitr)
library(kableExtra)
```

```{r}
df <- read_csv(here("data/processed/tradeoff_df.csv")) %>% 
  select(-matches("up_bird|all_bird"))

```

#### Data summary

Sites with ARU

```{r}
df %>% 
  filter(!is.na(wet_bird_richness)) %>% 
  pull(site) %>% 
  unique()
```

## Introduction

Wetlands provide critical ecosystem services

biodiversity

greenhouse gas sequestration

We are experiencing a dual global crisis: climate change and biodiversity loss. Despite the importance of these crises, we have limited resources to address both. Wetlands have increasingly been considered as a nature-based climate solution that can address both carbon (C) sequestration and biodiversity1. Temperate grasslands, such as the Prairie Pothole Region (PPR) of Canada have the highest density of wetlands globally2, yet these ecosystems are continually threatened by agricultural development3. For example, by 1970 over 1.2 million hectares of wetlands were lost to the expansion of agricultural land across the Canadian prairies4 with Ducks Unlimited Canada (DUC) estimating an additional 0.4 million hectares have been lost since then. As a result, conservation of these systems is critical to prevent further loss of habitat and for the potential of these systems to mitigate climate change and biodiversity decline. However, current hypotheses suggest that productivity of wetlands will set up a trade-off between biodiversity and C sequestration5,6. Though higher productivity in wetlands supports greater biodiversity7, the anoxic conditions of wetlands can result in high emissions of greenhouse gases (GHG) such as methane and CO<sub>2</sub>8,9. Conservation of wetlands may be threatened as these systems are seen as carbon emitters. Therefore, understanding trade-offs and identifying possible synergies between wetland productivity and biodiversity may promote their conservation while also addressing climate change and biodiversity loss.

#### Hypotheses

1.  We expect a positive relationship between emergent vegetation productivity, as aerial biomass, with both biodiversity and GHG fluxes.

### Data sets

This projects leverages several data sets collected across the PPR by DUC and the Bogard lab.

-   These include:
    -   emergent vegetation data

        -   drone imagery (2023)

        -   quadrat samples (2023)

            -   biomass
            -   nutrient content (N, P, K, S)
            -   dominant species

    -   GHG fluxes (2022 & 2023)

        -   CO<sub>2</sub>
        -   CH<sub>4</sub>
        -   N<sub>2</sub>O

    -   avian biodiversity (2022 & 2023)

### Outline

This document is separated into sections according to the data sets used as the response variable. The intention is to explore each data set to find patterns before settling on a final story for the manuscript.

## Emergent vegetation

Wetlands, unlike lakes and rivers, often have a greater ratio of shoreline to open water, promoting greater inputs of terrestrial materials to aquatic habitats13. These inputs fuel microbial respiration14 and sustained GHG emissions from aquatic habitats15,16 . While this story is becoming clear, the role of emergent plant production in offsetting these emissions is not well understood. The C sequestered by emergent vegetation may sufficiently offset emissions from aquatic habitats to render PPR wetlands "C neutral". Further, wetlands within agricultural landscapes may also experience higher nutrient loading from upland livestock or fertilizer applications, which may alter emission patterns17 by enhancing algal production and aquatic C uptake that may lower emissions (e.g., Bogard et al. 201718). Conversely, soil disturbance by cropping can transfer organics to wetlands that may fuel GHG emissions9.

To determine the productivity of emergent vegetation along the wetland edge I will use a combination of advanced remote sensing and traditional ground-based measures of biomass. Using uncrewed aerial vehicles (UAVs), I will collect high-resolution imagery of wetlands at the end of the growing season to produce robust images to estimate vegetation type and density24,25 . To differentiate landscape characteristics, spectral indices and methods including spatial clustering26 and machine learning27 will be used to identify the extent of emergent vegetation around each wetland. I will collect biomass samples from a subset of six wetlands (3 sites per wetlands) in each province28 . Biomass samples will be processed (weight, C content) using standard methods29 . We will estimate total emergent vegetation productivity by scaling spectral properties with biomass and C content and applying the relationship to the entire wetland surface.


## Methods

### Study sites

We focused on ???? wetlands across the Prairie Pothole Region (PPR) of Alberta and Saskatchewan ranging from ????° to ????° latitude (Add Map). The region is characterized by extreme temperature variability, ranging from semi-arid in summer to a cold continental climate in winter, low precipitation, and strong winds (Add Weather Data). Land use is dominated by agriculture. (Add more about topography and water drainage)

The ??? wetlands surveyed covered a diverse range of sizes and morphologies (depths??), ranging from small and shallow ponds (???? m<sup>2</sup> and ???? m) to large deep water bodies (???? m<sup>2</sup> and ???? m). Each site was sampled ???? times in the summer (Add date). (Add sampling for each analysis here or in the associated section)

```{r}
#| label: tbl-cars
#| tbl-cap-location: top
cor_df <- df %>% 
  cor_test(total_density, full_wetland_area_m2, starts_with("flux"), ends_with("richness")) 

cor_df %>%
  # remove duplicated pairs
  filter(!duplicated(paste0(pmax(var1, var2), pmin(var1, var2)))) %>% 
  # filter to only p <= 0.1
  filter(p <= 0.1) %>% 
  # remove correlation between identical variables
  filter(cor != 1) %>% 
  # remove where statistic is Inf
  filter(is.finite(statistic)) %>% 
  rename("Variable 1" = var1,
         "Variable 2" = var2,
         "r" = cor,
         "Statistic" = statistic, 
         "p value" = p,
         "Conf. low" = conf.low,
         "Conf. high" = conf.high,) %>%
  select(-method) %>% 
  mutate(across(where(is.numeric), \(x) round(x, 2))) %>%
  kbl(format = "markdown", caption = "Pearson correlation results") %>% 
  kable_styling(full_width = F)
  
  
  # kable(format = "markdown", caption = "Pearson correlation results") %>%
  # kable_classic("basic", full_width = F) %>%
  # row_spec(0, bold = T)
  
```

## Results

Emergent vegetation density correlations with GHG and richness

Correlation between GHG and richness

## Aquatic productivity

#### Does the amount of emergent vegetation control aquatic productivity?

```{r}
#| fig-height: 8

(((df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = full_wetland_area_m2, y = aerial_gpp)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 20)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = full_wetland_area_m2, y = aerial_r)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 20)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = full_wetland_area_m2, y = aerial_gpp - aerial_r)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "NEP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(-10, 2)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) | 
  
  ((df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_density, y = aerial_gpp)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  geom_smooth(method = "lm", se = F,
              linetype = "dashed", colour = "black") + 
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 20)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_density, y = aerial_r)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  geom_smooth(method = "lm", se = F, 
              colour = "black") + 
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 20)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_density, y = aerial_gpp - aerial_r)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "NEP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(-10, 2)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())))) + plot_layout(guides = "collect")
```

## GHG fluxes

#### Does the amount of emergent vegetation control aquatic productivity?

```{r}
#| fig-height: 10.66667
#| fig-width: 8
(((df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = full_wetland_area_m2, y = flux_co2)) +
  geom_point() +
  stat_correlation(use_label(c("R", "P")),
                   r.digits = 2, p.digits = 2,
                   small.r = T, small.p = T) + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0,300)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = full_wetland_area_m2, y = flux_ch4)) +
  geom_point() +
  stat_correlation(use_label(c("R", "P")),
                   r.digits = 2, p.digits = 2,
                   small.r = T, small.p = T) + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)", 
                     limits = c(0, 100)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = full_wetland_area_m2, y = flux_n2o)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") + 
  stat_correlation(use_label(c("R", "P")),
                   r.digits = 2, p.digits = 2,
                   small.r = T, small.p = T) + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(-0.01, 0.03)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) | 
  ((df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_density, y = flux_co2)) +
  geom_point() +
  stat_correlation(use_label(c("R", "P")),
                   r.digits = 2, p.digits = 2,
                   small.r = T, small.p = T) + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0,300)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_density, y = flux_ch4)) +
  geom_point() +
  geom_smooth(method = "lm", formula = "y ~ x", se = F, 
              colour = "grey75", linetype = "dashed") + 
  stat_correlation(use_label(c("R", "P")),
                   r.digits = 2, p.digits = 2,
                   small.r = T, small.p = T) + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)", 
                     limits = c(0, 100)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_density, y = flux_n2o)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") + 
  stat_correlation(use_label(c("R", "P")),
                   r.digits = 2, p.digits = 2,
                   small.r = T, small.p = T) + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)"
                     ,
                     limits = c(-0.01, 0.03)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())))) + plot_layout(guides = "collect")

```

#### Are aquatic productivity and GHG fluxes correlated?

```{r}
#| fig-height: 8
((df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_gpp, y = flux_co2)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0,300)) + 
  scale_x_continuous(name = "GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 15)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_gpp, y = flux_ch4)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +

  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0,100)) + 
  scale_x_continuous(name = "GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 15)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_gpp, y = flux_n2o)) +
  geom_point(aes(colour = land_class)) +
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 0.05)) + 
  scale_x_continuous(name = "GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 15)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) | 
  (df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_r, y = flux_co2)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0,300)) + 
  scale_x_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_r, y = flux_ch4)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +

  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0,100)) + 
  scale_x_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_r, y = flux_n2o)) +
  geom_point(aes(colour = land_class)) +
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 0.05)) + 
  scale_x_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) | 
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_gpp - aerial_r, y = flux_co2)) +
  geom_point(aes(colour = land_class)) +
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0,300)) + 
  scale_x_continuous(name = "NEP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(-10, 2),
                     breaks = seq(-10, 2, 4)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_gpp - aerial_r, y = flux_ch4)) +
  geom_point(aes(colour = land_class)) +
  geom_smooth(method = "lm", se = F,
              linetype = "dashed", colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +

  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0,100)) + 
  scale_x_continuous(name = "NEP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(-10, 2),
                     breaks = seq(-10, 2, 4)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_gpp - aerial_r, y = flux_n2o)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 0.05)) + 
  scale_x_continuous(name = "NEP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(-10, 2),
                     breaks = seq(-10, 2, 4)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) + plot_layout(guides = "collect")
```

## Biodiversity


#### Does higher of emergent vegetation increase biodiversity?

```{r}
#| fig-height: 3.5
#| fig-width: 8
(df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = total_mass_Mg, y = wet_bird_richness)) +
  geom_point() +
  stat_correlation(use_label(c("R", "P")),
                   r.digits = 2, p.digits = 2,
                   small.r = T, small.p = T) + 
  scale_y_continuous(name = "Wetland bird richness",
                     limits = c(0, 50)) + 
  scale_x_continuous(name = "Total biomass (Mg)",
                     limits = c(0, 25)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) |

(df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = full_wetland_area_m2, y = wet_bird_richness)) +
  geom_point() +
  stat_correlation(use_label(c("R", "P")),
                   r.digits = 2, p.digits = 2,
                   small.r = T, small.p = T) + 
  scale_y_continuous(name = "Wetland bird richness",
                     limits = c(0, 50)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000), 
                     breaks = seq(0, 80000, 40000)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_blank(),
        axis.title.x = element_markdown())) | 


(df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = total_density, y = wet_bird_richness)) +
  geom_point() +
  stat_correlation(use_label(c("R", "P")),
                   r.digits = 2, p.digits = 2,
                   small.r = T, small.p = T) + 
  scale_y_continuous(name = "Wetland bird richness",
                     limits = c(0, 50)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_blank(),
        axis.title.x = element_markdown()))
  
```

#### Does aquatic productivity support higher avian biodiversity?

```{r}

(((df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_gpp, y = wet_bird_richness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird richness",
                     limits = c(0, 50)) + 
  scale_x_continuous("GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_gpp, y = wet_bird_evenness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird evenness",
                     limits = c(0.8, 1.1)) + 
  scale_x_continuous("GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) |


((df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_r, y = wet_bird_richness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird richness",
                     limits = c(0, 50)) + 
  scale_x_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                      limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_r, y = wet_bird_evenness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird evenness",
                     limits = c(0.8, 1.1)) + 
  scale_x_continuous(name ="R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                      limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) | 


((df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_gpp - aerial_r, y = wet_bird_richness)) +
  geom_point(aes(colour = land_class)) +
  geom_smooth(method = "lm", se = F,
              linetype = "dashed", colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird richness",
                     limits = c(0, 50)) + 
  scale_x_continuous(name = "NEP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(-10, 2)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_gpp - aerial_r, y = wet_bird_evenness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird evenness",
                     limits = c(0.8, 1.1)) + 
  scale_x_continuous(name = "NEP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(-10, 2)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())))) + plot_layout(guides = "collect")
```

#### Does higher diversity increase GHG fluxes?

```{r}
#| fig-height: 6
#| fig-width: 6
(df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_richness, y = flux_co2)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  stat_correlation(use_label(c("R", "P")),
                   r.digits = 2, p.digits = 2,
                   small.r = T, small.p = T) + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 400)) + 
  scale_x_continuous(name = "Wetland bird richness",
                     limits = c(10, 40)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
  
  (df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_richness, y = flux_ch4)) + 
  geom_point() + 
  stat_correlation(use_label(c("R", "P")),
                   r.digits = 2, p.digits = 2,
                   small.r = T, small.p = T) + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0,150)) + 
  scale_x_continuous(name = "Wetland bird richness",
                     limits = c(10, 40)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) / 
  
  (df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_richness, y = flux_n2o)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  stat_correlation(use_label(c("R", "P")),
                   r.digits = 2, p.digits = 2,
                   small.r = T, small.p = T) + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0,0.06)) + 
  scale_x_continuous(name = "Wetland bird richness",
                     limits = c(10, 40)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))

```
