---
title: "Tradeoffs between PPR carbon sequestration and biodiversity"
author:
  - name: Samuel G. Woodman
    orcid: 0000-0001-9725-5867
    email: samuel.woodman@uleth.ca
    corresponding: true
    affiliation: 
      - name: University of Lethbridge
  - name: Lauren E. Bortolotti
    email: l_bortolotti@ducks.ca
    corresponding: false
    affiliation: 
      - name: Ducks Unlimited Canada
  - name: James E. Paterson
    email: j_paterson@ducks.ca
    corresponding: false
    affiliation: 
      - name: Ducks Unlimited Canada
  - name: Pascal Badiou
    email: p_badiou@ducks.ca
    corresponding: false
    affiliation: 
      - name: Ducks Unlimited Canada
  - name: Matthew J Bogard
    email: matthew.bogard@uleth.ca
    corresponding: false
    affiliation: 
      - name: University of Lethbridge
format:
  html:
    toc: true
    toc-location: left
    comments:
      hypothesis: true
    embed-resources: true
  docx: default
  pdf: default
editor: visual
editor_options: 
  chunk_output_type: console
execute: 
  echo: false
  warning: false
---

```{r}
library(tidyverse)
library(here)
library(ggtext)
library(patchwork)
library(ggpubr)
library(gridtext)
library(ggpmisc)
```

```{r}
df <- read_csv(here("data/processed/tradeoff_df.csv"))

```

## Introduction

We are experiencing a dual global crisis: climate change and biodiversity loss. Despite the importance of these crises, we have limited resources to address both. Wetlands have increasingly been considered as a nature-based climate solution that can address both carbon (C) sequestration and biodiversity1. Temperate grasslands, such as the Prairie Pothole Region (PPR) of Canada have the highest density of wetlands globally2, yet these ecosystems are continually threatened by agricultural development3. For example, by 1970 over 1.2 million hectares of wetlands were lost to the expansion of agricultural land across the Canadian prairies4 with Ducks Unlimited Canada (DUC) estimating an additional 0.4 million hectares have been lost since then. As a result, conservation of these systems is critical to prevent further loss of habitat and for the potential of these systems to mitigate climate change and biodiversity decline. However, current hypotheses suggest that productivity of wetlands will set up a trade-off between biodiversity and C sequestration5,6. Though higher productivity in wetlands supports greater biodiversity7, the anoxic conditions of wetlands can result in high emissions of greenhouse gases (GHG) such as methane and CO28,9. Conservation of wetlands may be threatened as these systems are seen as carbon emitters. Therefore, understanding trade-offs and identifying possible synergies between wetland productivity and biodiversity may promote their conservation while also addressing climate change and biodiversity loss.

### Data sets

This projects leverages several data sets collected across the PPR by DUC and the Bogard lab.

-   These include:
    -   emergent vegetation data

        -   drone imagery (2023)

        -   quadrat samples (2023)

            -   biomass
            -   nutrient content (N, P, K, S)
            -   dominant species

    -   aquatic productivity (2022 & 2023)

        -   GPP
        -   R

    -   GHG fluxes (2022 & 2023)

        -   CO<sub>2</sub>
        -   CH<sub>4</sub>
        -   N<sub>2</sub>O

    -   avian biodiversity (2022 & 2023)

### Outline

This document is separated into sections according to the data sets used as the response variable. The intention is to explore each data set to find patterns before settling on a final story for the manuscript.

## Emergent vegetation

Wetlands, unlike lakes and rivers, often have a greater ratio of shoreline to open water, promoting greater inputs of terrestrial materials to aquatic habitats13. These inputs fuel microbial respiration14 and sustained GHG emissions from aquatic habitats15,16 . While this story is becoming clear, the role of emergent plant production in offsetting these emissions is not well understood. The C sequestered by emergent vegetation may sufficiently offset emissions from aquatic habitats to render PPR wetlands "C neutral". Further, wetlands within agricultural landscapes may also experience higher nutrient loading from upland livestock or fertilizer applications, which may alter emission patterns17 by enhancing algal production and aquatic C uptake that may lower emissions (e.g., Bogard et al. 201718). Conversely, soil disturbance by cropping can transfer organics to wetlands that may fuel GHG emissions9.

To determine the productivity of emergent vegetation along the wetland edge I will use a combination of advanced remote sensing and traditional ground-based measures of biomass. Using uncrewed aerial vehicles (UAVs), I will collect high-resolution imagery of wetlands at the end of the growing season to produce robust images to estimate vegetation type and density24,25 . To differentiate landscape characteristics, spectral indices and methods including spatial clustering26 and machine learning27 will be used to identify the extent of emergent vegetation around each wetland. I will collect biomass samples from a subset of six wetlands (3 sites per wetlands) in each province28 . Biomass samples will be processed (weight, C content) using standard methods29 . We will estimate total emergent vegetation productivity by scaling spectral properties with biomass and C content and applying the relationship to the entire wetland surface.

#### How does land use impact the productivity of emergent vegetation?

```{r}
((df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = land_class, y = total_mass_Mg, 
             fill = land_class)) + 
  geom_boxplot() + 
  scale_fill_manual(values = c("#4fad3c","#f4be4a")) + 
  scale_y_continuous(name = "Total biomass (Mg)") + 
  theme_classic2() + 
  theme(axis.title.x = element_blank(), 
        legend.position = 'none')) / 
(df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = land_class, y = full_wetland_area_m2, 
             fill = land_class)) + 
  geom_boxplot() + 
  scale_fill_manual(values = c("#4fad3c","#f4be4a")) + 
  scale_y_continuous(name = "Wetland area (m<sup>-2</sup>)") + 
  theme_classic2() + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_markdown(),
        legend.position = 'none'))) | 
df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = land_class, y = total_density, 
             fill = land_class)) + 
  geom_boxplot() + 
  scale_fill_manual(values = c("#4fad3c","#f4be4a")) + 
  scale_y_continuous(name = "Density of wetland emergent vegetation (kg m<sup>-2</sup>)") + 
  theme_classic2() + 
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_markdown(),
        legend.position = 'none')
```

#### Are difference in land use driven by latitude?

```{r}
df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = latitude, y = total_mass_Mg, 
             colour = land_class)) + 
  geom_point() + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) + 
  scale_y_continuous(name = "Total biomass (Mg)") + 
  scale_x_continuous(name = "Latitude (°)", 
                     limits = c(53.075, 53.2)) + 
  theme_classic2() + 
  theme(legend.position = 'top')
```

### Aquatic productivity

#### Does aquatic productivity differ with land use?

```{r}
(df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = land_class, y = aerial_gpp, 
             fill = land_class)) + 
  geom_boxplot() + 
  scale_fill_manual(values = c("#4fad3c","#f4be4a")) + 
  scale_y_continuous(name = "GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.x = element_blank(), 
        legend.position = 'none',
        axis.title.y = element_markdown())) + 
  (df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = land_class, y = aerial_r, 
             fill = land_class)) + 
  geom_boxplot() + 
  scale_fill_manual(values = c("#4fad3c","#f4be4a")) + 
  scale_y_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                      limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.x = element_blank(), 
        legend.position = 'none',
        axis.title.y = element_markdown()))
```

#### Does the amount of emergent vegetation control aquatic productivity?

```{r}
#| fig.height: 6
#| fig-width: 10
(((df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_mass_Mg, y = aerial_gpp)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 16)) + 
  scale_x_continuous(name = "Total biomass (Mg)",
                     limits = c(0, 25)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_mass_Mg, y = aerial_r)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  geom_smooth(method = "lm", se = F, 
              linetype = "dashed", colour = "black") + 
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 16)) + 
  scale_x_continuous(name = "Total biomass (Mg)",
                     limits = c(0, 25)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) |

((df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = full_wetland_area_m2, y = aerial_gpp)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 16)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = full_wetland_area_m2, y = aerial_r)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 16)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) | 
  
  ((df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_density, y = aerial_gpp)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  geom_smooth(method = "lm", se = F,
              linetype = "dashed", colour = "black") + 
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 16)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_density, y = aerial_r)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  geom_smooth(method = "lm", se = F, 
              colour = "black") + 
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 16)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())))) + plot_layout(guides = "collect")
```

### GHG fluxes

#### Do fluxes of GHG gases differ with land use?

```{r}

(df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = land_class, y = flux_co2, 
             fill = land_class)) + 
  geom_boxplot() + 
  scale_fill_manual(values = c("#4fad3c","#f4be4a")) + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  theme_classic2() + 
  theme(axis.title.x = element_blank(), 
        legend.position = 'none',
        axis.title.y = element_markdown())) + 
  (df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = land_class, y = flux_ch4, 
             fill = land_class)) + 
  geom_boxplot() + 
  scale_fill_manual(values = c("#4fad3c","#f4be4a")) + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  theme_classic2() + 
  theme(axis.title.x = element_blank(), 
        legend.position = 'none',
        axis.title.y = element_markdown())) + 
  (df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = land_class, y = flux_n2o, 
             fill = land_class)) + 
  geom_boxplot() + 
  scale_fill_manual(values = c("#4fad3c","#f4be4a")) + 
  scale_y_continuous(name = "N<sub>4</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  theme_classic2() + 
  theme(axis.title.x = element_blank(), 
        legend.position = 'none',
        axis.title.y = element_markdown()))

```

#### Does the amount of emergent vegetation control aquatic productivity?

```{r}
#| fig-height: 6
#| fig-width: 10
(((df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_mass_Mg, y = flux_co2)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Total biomass (Mg)",
                     limits = c(0, 25)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_mass_Mg, y = flux_ch4)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Total biomass (Mg)",
                     limits = c(0, 25)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_mass_Mg, y = flux_n2o)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Total biomass (Mg)",
                     limits = c(0, 25)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) |

((df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = full_wetland_area_m2, y = flux_co2)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = full_wetland_area_m2, y = flux_ch4)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = full_wetland_area_m2, y = flux_n2o)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) | 
  ((df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_density, y = flux_co2)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_density, y = flux_ch4)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  geom_smooth(method = "lm", se = F, 
              colour = "black") + 
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = total_density, y = flux_n2o)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())))) + plot_layout(guides = "collect")

```

```{r}
#| fig-height: 8

  
```

#### Are aquatic productivity and GHG fluxes correlated?

```{r}
#| fig-height: 8
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_gpp, y = flux_co2)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 15)) + 
  theme_classic2() + 
  theme(legend.position = 'top',
        axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_gpp, y = flux_ch4)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +

  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 15)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_gpp, y = flux_n2o)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 15)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) | 
  (df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_r, y = flux_co2)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(legend.position = 'top',
        axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_r, y = flux_ch4)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +

  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
(df %>%
  filter(land_class != "Both") %>% 
  ggplot(aes(x = aerial_r, y = flux_n2o)) +
  geom_point(aes(colour = land_class)) +
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(legend.position = 'none',
        axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))
```

### Biodiversity

#### How does land use impact biodiversity

```{r}
#| fig-height: 10
#| fig-width: 8
((df %>% 
  pivot_longer(cols = ends_with("richness"), 
               names_to = "group", 
               values_to = "rich") %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = land_class, y = rich, fill = land_class)) + 
  geom_boxplot() + 
  scale_y_continuous(name = "Richness") + 
  scale_fill_manual(values = c("#4fad3c","#f4be4a")) + 
  facet_wrap(~group, scales = "free_y") + 
  theme_classic2() + 
  theme(axis.title.x = element_blank(), 
        legend.position = 'none',
        axis.title.y = element_markdown())) + 

(df %>% 
  pivot_longer(cols = ends_with("evenness"), 
               names_to = "group", 
               values_to = "even") %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = land_class, y = even, fill = land_class)) + 
  geom_boxplot() + 
  scale_y_continuous(name = "Evenness") + 
  scale_fill_manual(values = c("#4fad3c","#f4be4a")) + 
  facet_wrap(~group, scales = "free_y") + 
  theme_classic2() + 
  theme(axis.title.x = element_blank(), 
        legend.position = 'none',
        axis.title.y = element_markdown()))) /

((df %>% 
  pivot_longer(cols = ends_with("shannon"), 
               names_to = "group", 
               values_to = "shan") %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = land_class, y = shan, fill = land_class)) + 
  geom_boxplot() + 
  scale_y_continuous(name = "Shannon index") + 
  scale_fill_manual(values = c("#4fad3c","#f4be4a")) + 
  facet_wrap(~group, scales = "free_y") + 
  theme_classic2() + 
  theme(axis.title.x = element_blank(), 
        legend.position = 'none',
        axis.title.y = element_markdown())) +

(df %>% 
  pivot_longer(cols = ends_with("simpson"), 
               names_to = "group", 
               values_to = "simp") %>% 
  filter(land_class != "Both") %>% 
  filter(!str_detect(group, "unbias|inverse")) %>% 
  ggplot(aes(x = land_class, y = simp, fill = land_class)) + 
  geom_boxplot() + 
  scale_y_continuous(name = "Simpson index") + 
  scale_fill_manual(values = c("#4fad3c","#f4be4a")) + 
  facet_wrap(~group, scales = "free_y") + 
  theme_classic2() + 
  theme(axis.title.x = element_blank(), 
        legend.position = 'none',
        axis.title.y = element_markdown())))
```

#### Does higher of emergent vegetation increase biodiversity?

```{r}
#| fig-height: 10
#| fig-width: 10
(((df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = total_mass_Mg, y = wet_bird_richness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird richness",
                     limits = c(0, 50)) + 
  scale_x_continuous(name = "Total biomass (Mg)",
                     limits = c(0, 25)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = total_mass_Mg, y = wet_bird_evenness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird evenness",
                     limits = c(0.8, 1.1)) + 
  scale_x_continuous(name = "Total biomass (Mg)",
                     limits = c(0, 25)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = total_mass_Mg, y = wet_bird_shannon)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird shannon index",
                     limits = c(2.5, 4.5)) + 
  scale_x_continuous(name = "Total biomass (Mg)",
                     limits = c(0, 25)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = total_mass_Mg, y = wet_bird_simpson)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird simpson index",
                     limits = c(0.9, 1.1)) + 
  scale_x_continuous(name = "Total biomass (Mg)",
                     limits = c(0, 25)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) |


((df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = full_wetland_area_m2, y = wet_bird_richness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird richness",
                     limits = c(0, 50)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = full_wetland_area_m2, y = wet_bird_evenness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird evenness",
                     limits = c(0.8, 1.1)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = full_wetland_area_m2, y = wet_bird_shannon)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird shannon index",
                     limits = c(2.5, 4.5)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = full_wetland_area_m2, y = wet_bird_simpson)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird simpson index",
                     limits = c(0.9, 1.1)) + 
  scale_x_continuous(name = "Wetland area (m<sup>-2</sup>)",
                     limits = c(0, 80000)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) | 


((df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = total_density, y = wet_bird_richness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird richness",
                     limits = c(0, 50)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = total_density, y = wet_bird_evenness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird evenness",
                     limits = c(0.8, 1.1)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = total_density, y = wet_bird_shannon)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird shannon index",
                     limits = c(2.5, 4.5)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_blank())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = total_density, y = wet_bird_simpson)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird simpson index",
                     limits = c(0.9, 1.1)) + 
  scale_x_continuous(name = "Density of wetland emergent<br>vegetation (kg m<sup>-2</sup>)",
                     limits = c(0, 0.6)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())))) + plot_layout(guides = "collect")
  
```

#### Does aquatic productivity support higher avian biodiversity?

```{r}
#| fig-height: 10
#| fig-width: 10
(((df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_gpp, y = wet_bird_richness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird richness",
                     limits = c(0, 50)) + 
  scale_x_continuous("GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_gpp, y = wet_bird_evenness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird evenness",
                     limits = c(0.8, 1.1)) + 
  scale_x_continuous("GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_gpp, y = wet_bird_shannon)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird shannon index",
                     limits = c(2.5, 4.5)) + 
  scale_x_continuous("GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_gpp, y = wet_bird_simpson)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird simpson index",
                     limits = c(0.9, 1.1)) + 
  scale_x_continuous("GPP<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) |


((df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_r, y = wet_bird_richness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird richness",
                     limits = c(0, 50)) + 
  scale_x_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                      limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_r, y = wet_bird_evenness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird evenness",
                     limits = c(0.8, 1.1)) + 
  scale_x_continuous(name ="R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                      limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_r, y = wet_bird_shannon)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird shannon index",
                     limits = c(2.5, 4.5)) + 
  scale_x_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                      limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_r, y = wet_bird_simpson)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird simpson index",
                     limits = c(0.9, 1.1)) + 
  scale_x_continuous(name = "R<sub>*aq*</sub> (g O<sub>2</sub> m<sup>-2</sup> d<sup>-1</sup>)",
                      limits = c(0, 22)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) | 


((df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_gpp/aerial_r, y = wet_bird_richness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird richness",
                     limits = c(0, 50)) + 
  scale_x_continuous(name = "GPP:R") + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_gpp/aerial_r, y = wet_bird_evenness)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird evenness",
                     limits = c(0.8, 1.1)) + 
  scale_x_continuous(name = "GPP:R") + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_gpp/aerial_r, y = wet_bird_shannon)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird shannon index",
                     limits = c(2.5, 4.5)) + 
  scale_x_continuous(name = "GPP:R") + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) /
  (df %>%
  filter(land_class != "Both") %>%
  ggplot(aes(x = aerial_gpp/aerial_r, y = wet_bird_simpson)) +
  geom_point(aes(colour = land_class)) +
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "Wetland bird simpson index",
                     limits = c(0.9, 1.1)) + 
  scale_x_continuous(name = "GPP:R") + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())))) + plot_layout(guides = "collect")
```

#### Does higher diversity increase GHG fluxes?

```{r}
#| fig-height: 8
#| fig-width: 10
(((df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_richness, y = flux_co2)) + 
  geom_point(aes(colour = land_class)) + 
  geom_smooth(method = "lm", se = F,
              linetype = "dashed", colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 300)) + 
  scale_x_continuous(name = "Wetland bird richness",
                     limits = c(10, 40)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) |
  (df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_evenness, y = flux_co2)) + 
  geom_point(aes(colour = land_class)) + 
  geom_smooth(method = "lm", se = F,
              linetype = "dashed", colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 300)) + 
  scale_x_continuous(name = "Wetland bird evenness",
                     limits = c(0.7, 1.1)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) /
  
  ((df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_richness, y = flux_ch4)) + 
  geom_point(aes(colour = land_class)) + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Wetland bird richness",
                     limits = c(10, 40)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) |
  (df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_evenness, y = flux_ch4)) + 
  geom_point(aes(colour = land_class)) + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Wetland bird evenness",
                     limits = c(0.7, 1.1)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) / 
  
  ((df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_richness, y = flux_n2o)) + 
  geom_point(aes(colour = land_class)) + 
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Wetland bird richness",
                     limits = c(10, 40)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) |
  (df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_evenness, y = flux_n2o)) + 
  geom_point(aes(colour = land_class)) + 
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Wetland bird evenness",
                     limits = c(0.7, 1.1)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())))) + plot_layout(guides = "collect")
  
  
(((df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_shannon, y = flux_co2)) + 
  geom_point(aes(colour = land_class)) + 
  geom_smooth(method = "lm", se = F,
              linetype = "dashed", colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 300)) + 
  scale_x_continuous(name = "Wetland bird shannon index",
                     limits = c(2.5, 3.75)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) |
  (df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_simpson, y = flux_co2)) + 
  geom_point(aes(colour = land_class)) + 
  geom_smooth(method = "lm", se = F,
              linetype = "dashed", colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CO<sub>2 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)",
                     limits = c(0, 300)) + 
  scale_x_continuous(name = "Wetland bird simpson index",
                     limits = c(0.9, 1)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) /
  
  ((df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_shannon, y = flux_ch4)) + 
  geom_point(aes(colour = land_class)) + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Wetland bird shannon index",
                     limits = c(2.5, 3.75)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) |
  (df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_simpson, y = flux_ch4)) + 
  geom_point(aes(colour = land_class)) + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "CH<sub>4 *aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Wetland bird simpson index",
                     limits = c(0.9, 1)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown()))) / 
  
  ((df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_shannon, y = flux_n2o)) + 
  geom_point(aes(colour = land_class)) + 
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Wetland bird shannon index",
                     limits = c(2.5, 3.75)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())) |
  (df %>% 
  filter(land_class != "Both") %>% 
  ggplot(aes(x = wet_bird_simpson, y = flux_n2o)) + 
  geom_point(aes(colour = land_class)) + 
  geom_smooth(method = "lm", se = F,
              colour = "black") + 
  scale_colour_manual(name = "Land Use",
                      values = c("#4fad3c","#f4be4a")) +
  stat_poly_eq(mapping = use_label(c("adj.R2", "p.value")),
               rr.digits = 2, p.digits = 2, small.p = T, 
               colour = "black") + 
  scale_y_continuous(name = "N<sub>2</sub>O <sub>*aq*</sub> (mmol m<sup>-2</sup> d<sup>-1</sup>)") + 
  scale_x_continuous(name = "Wetland bird simpson index",
                     limits = c(0.9, 1)) + 
  theme_classic2() + 
  theme(axis.title.y = element_markdown(),
        axis.title.x = element_markdown())))) + plot_layout(guides = "collect")
```
